---
title: "Team"
author: "McKenna Goffinet & Anyesha Ray"
date: "2/5/2020"
output:
  pdf_document: default
  html_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
choco <- read.csv("https://xdaiisu.github.io/ds202materials/hwlabs/choco.csv")
library(plyr)
```

1)
```{r}
dim(choco)
head(choco)
```
1852 chocolate bars

2)
```{r}
barplot(table(choco$Review.Date))
```
The number of ratings per year has been generally increasing over the years, though inconsistently. The number of ratings in a single year peaked in 2015, followed by a sudden drop in 2017. The period of most increase occurred during the years of 2010 to 2015.

3)
```{r}
y <- count(choco$Company)
z <- y[order(-y$freq),]
z[1:3,]


boxplot(choco$Rating~choco$Company.Location, main="Country Location vs. Rating", xlab="Country Location", ylab="Rating")

```


Location does not seem to have much of an impact on rating. They seem pretty consistedn in the 2 to 4 rating range with a few outliers. 

4)
Our Question:
What are the most popular countries for producing beans? What are the least 3?

5)
Most popular:
```{r}
c <- count(choco$Broad.Bean.Origin)
d <- c[order(-c$freq),]
d[1:3,]
```
Least popular:
```{r}
e <- count(choco$Broad.Bean.Origin)
f <- e[order(e$freq),]
f[1:10,]
```

6)
Since we did this in lab, the workflow was smooth. We both worked on question 1 to 3 on Mckenna's laptop and then pushed it. We worked on the last 3 questions on my laptop. It was pretty balanced work load but it is slightly difficult to push and pull items from Github at least at this stage. Other wise work flow was smooth. We both did the individual part and then collaborated on the team questions on both laptops.  